SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-07-26 scipy-1.0/paper.tex
Address review comments of @mdhaber on scope section.

\textbf{Project scope}
SciPy aims to provide fundamental algorithms for scientific computing. The
breadth of its scope was derived from the Guide to Available Mathematical
Software classification system (GAMS\cite{boisvert1991guide}). In areas
that move relatively slowly, e.g. linear algebra, SciPy aims to provide
complete coverage. In other areas it aims to provide fundamental building
blocks, while interacting well with other packages specialized in that area.
For example for statistics, SciPy provides what one expect to find in a
statistics textbook (probability distributions, hypothesis tests, frequency
statistics, correlation functions, and more), while Statsmodels provides
more advanced statistical estimators and inference methods, scikit-learn
covers machine learning, PyMC3, emcee and PyStan cover Bayesian statistics
and probabilistic modelling.

We use the following criteria to determine whether or not to include new
functionality in SciPy:
\begin{itemize}
    \item The algorithm is of relevance to multiple fields of science.
    \item The implementation is demonstrably important.  E.g., it is classic
    enough to be included in textbooks, or it is based on a peer-reviewed article
    which has a significant number of citations.
\end{itemize}

>>>>

\textbf{Project scope}
SciPy aims to provide fundamental algorithms for scientific computing. The
breadth of its scope was derived from the Guide to Available Mathematical
Software classification system (GAMS\cite{boisvert1991guide}). In areas
that move relatively slowly, e.g. linear algebra, SciPy aims to provide
complete coverage. In other areas it aims to provide fundamental building
blocks while interacting well with other packages specialized in that area.
For example, SciPy provides what one expect to find in a
statistics textbook (probability distributions, hypothesis tests, frequency
statistics, correlation functions, and more), while Statsmodels provides
more advanced statistical estimators and inference methods, scikit-learn
covers machine learning, PyMC3, emcee and PyStan cover Bayesian statistics
and probabilistic modelling.

We use the following criteria to determine whether or not to include new
functionality in SciPy:
\begin{itemize}
    \item The algorithm is of relevance to multiple fields of science.
    \item The algorithm is demonstrably important.  E.g., it is classic
    enough to be included in textbooks, or it is based on a peer-reviewed article
    which has a significant number of citations.
\end{itemize}
